Investigations of the galaxies of the LCV

### 2023-07-23 paper2.tex
I recompiled (i think thats all)

% Created 2023-06-10 Sat 19:05
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{breakcites}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage{tgbonum}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\author{Dimitrios Papachistopoulos}
\date{\today}
\title{Investigations of the galaxies of the LCV}
\hypersetup{
 pdfauthor={Dimitrios Papachistopoulos},
 pdftitle={Investigations of the galaxies of the LCV},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

@@

\subsection{{\bfseries\sffamily TODO} no indent}
\label{sec:org4ae1c6d}
\subsection{{\bfseries\sffamily TODO} fullstops}
\label{sec:orge244364}
\subsection{{\bfseries\sffamily TODO} Units in the plots}
\label{sec:orgaf69437}

@@

\section{The Galaxies in the Local Cosmological Volume (LCV)}
\label{sec:org94f634b}

@@

\section{Types of galaxies}
\label{sec:org1701b4d}

@@

\subsection{{\bfseries\sffamily TODO} write a table with the types}
\label{sec:org421f46e}

@@

\section{Delayed-\(\tau\) model}
\label{sec:org57c1611}

@@

\subsection{Constant \(t_{sf}\)}
\label{sec:org4a83115}
The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).

@@

\subsection{Constant \(\tau\)}
\label{sec:org7264b82}

@@

\subsection{Comparing the two results}
\label{sec:orgd5edef3}

\subsubsection{Comparing the \(x\)'s}
\label{sec:orgd408258}

@@

\subsubsection{Comparing the normalization constants}
\label{sec:org976880e}

@@

\subsubsection{Trying to make the A\textsubscript{del} cloud more compact}
\label{sec:orge02c923}

@@

\subsection{Int SFR to find the A\textsubscript{del}}
\label{sec:org2f66940}

@@

\subsection{Calculating the \(t_{sf}\) and \(\tau\) for each galaxy}
\label{sec:org38a8c66}

@@

\subsubsection{[?]}
\label{sec:org2822411}
\begin{itemize}
\item Can we calculate/observe \(\zeta\)?
\begin{itemize}
\item If not: for galaxies with extreme star-bursting and low-metallicity galaxies \(\zeta=2-3\). Can we find those galaxies and approximate the \(\zeta\)?
\end{itemize}
\item Why couldn't we use (\ref{eq:av_SFR M*}) to calculate \(A_{del}\)
\item While in the second method we see a better correlation between the age of the galaxy and the color index, we must have an older universe
\end{itemize}

\section{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
\label{sec:org873dcd6}

@@

\section{Mass relations}
\label{sec:org1e2130d}

@@

\section{Variations in Star Formation Rate Across the Different Masses}
\label{sec:org64de891}

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-log_tau_g-color_logStellarMass.png}
\caption{\label{fig:None}None}
\end{figure}
\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_SFR_0-color_log_tau_g.png}
\caption{\label{fig:None}None}
\end{figure}
(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7fbf61cc5a10>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
\includegraphics[width=.9\linewidth]{./figs/logMt-log_tau-color_log_tau_g.png}
\end{center}', 'logMt-log\textsubscript{tau}-color\textsubscript{log}\textsubscript{tau}\textsubscript{g}')

(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7fbf61ee6b10>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
\includegraphics[width=.9\linewidth]{./figs/logMt-log_tsf-color_log_tau_g.png}
\end{center}', 'logMt-log\textsubscript{tsf}-color\textsubscript{log}\textsubscript{tau}\textsubscript{g}')

\subsection{{\bfseries\sffamily TODO} put that tau and tsf dont have a correlation with Mt}
\label{sec:org9a06924}

>>>>

% Created 2023-07-07 Fri 02:20
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{breakcites}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage{tgbonum}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\author{Dimitrios Papachistopoulos}
\date{\today}
\title{Investigations of the galaxies of the LCV}
\hypersetup{
 pdfauthor={Dimitrios Papachistopoulos},
 pdftitle={Investigations of the galaxies of the LCV},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

@@

\subsection{{\bfseries\sffamily TODO} no indent}
\label{sec:org2c76487}
\subsection{{\bfseries\sffamily TODO} fullstops}
\label{sec:org2eb98c4}
\subsection{{\bfseries\sffamily TODO} Units in the plots}
\label{sec:orge067e52}

@@

\section{The Galaxies in the Local Cosmological Volume (LCV)}
\label{sec:orgdd9bb01}

@@

\section{Types of galaxies}
\label{sec:org27414b8}

@@

\subsection{{\bfseries\sffamily TODO} write a table with the types}
\label{sec:org8b9d595}

@@

\section{Delayed-\(\tau\) model}
\label{sec:org7dfc126}

@@

\subsection{Constant \(t_{sf}\)}
\label{sec:orgdbc251f}
The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).

@@

\subsection{Constant \(\tau\)}
\label{sec:org2ca7572}

@@

\subsection{Comparing the two results}
\label{sec:org88a6937}

\subsubsection{Comparing the \(x\)'s}
\label{sec:org148b753}

@@

\subsubsection{Comparing the normalization constants}
\label{sec:org43d0c9b}

@@

\subsubsection{Trying to make the A\textsubscript{del} cloud more compact}
\label{sec:orgc5da7e1}

@@

\subsection{Int SFR to find the A\textsubscript{del}}
\label{sec:org6191eb1}

@@

\subsection{Calculating the \(t_{sf}\) and \(\tau\) for each galaxy}
\label{sec:org10a2834}

@@

\subsubsection{[?]}
\label{sec:org88e1de2}
\begin{itemize}
\item Can we calculate/observe \(\zeta\)?
\begin{itemize}
\item If not: for galaxies with extreme star-bursting and low-metallicity galaxies \(\zeta=2-3\). Can we find those galaxies and approximate the \(\zeta\)?
\end{itemize}
\item Why couldn't we use (\ref{eq:av_SFR M*}) to calculate \(A_{del}\)
\item While in the second method we see a better correlation between the age of the galaxy and the color index, we must have an older universe
\end{itemize}

\section{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
\label{sec:org4223423}

@@

\section{Mass relations}
\label{sec:orgb9a30c1}

@@

\section{Variations in Star Formation Rate Across the Different Masses}
\label{sec:orge561d63}

@@

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-log_tau_g-color_logStellarMass.png}
\caption{\label{fig:None}None}
\end{figure}
\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_SFR_0-color_log_tau_g.png}
\caption{\label{fig:None}None}
\end{figure}
(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7f234887cd50>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
\includegraphics[width=.9\linewidth]{./figs/logMt-log_tau-color_log_tau_g.png}
\end{center}', 'logMt-log\textsubscript{tau}-color\textsubscript{log}\textsubscript{tau}\textsubscript{g}')

(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7f23664ba6d0>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
\includegraphics[width=.9\linewidth]{./figs/logMt-log_tsf-color_log_tau_g.png}
\end{center}', 'logMt-log\textsubscript{tsf}-color\textsubscript{log}\textsubscript{tau}\textsubscript{g}')

\subsection{{\bfseries\sffamily TODO} put that tau and tsf dont have a correlation with Mt}
\label{sec:org8125488}
